Topic 21 Experiment and analysis

### 2018-05-16 Meetings/AnalysisMeetingMay2018/analysis_meeting2018_topic21.tex
update to script for Figure and TeX
Update to script for the comparison of H-Mode on AUG and corresponding description on TeX file

      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}

@@

      \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
      \includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
      \includegraphics<11>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantBt}
      % \includegraphics<11>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         

@@

          current in the far SOL \onslide<10>{\alert{but once evolution \textit{vs} greenwald

@@

        \item<only@11> Amplitude evolution still reconciled in AUG if

@@

        % \item<11|only@11> For both AUG and TCV $\lambda_n$ increases
        %   with blob size without significant difference within the
        %   current explored

@@

% \begin{frame}{Current scan at constant q$_{95}$}
%   \begin{columns}
%     \begin{column}{0.6\textwidth}
%       \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
%       \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
%       \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
%       \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantQ95}
%       \includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantQ95}
%       \includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}
%       \includegraphics<7>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantQ95}
%       \includegraphics<8>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldVBlobAllColorConstantQ95}         
%       \includegraphics<9>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/BlobLambdaAllColorConstantQ95}         
%     \end{column}
%     \begin{column}{0.4\textwidth}
%       \begin{itemize}
%         \item<1|only@1> Shape matched in within the single scan even
%           though this required for TCV operation with very low
%           toroidal field (0.8T)
%         \item<1|only@1> The parallel connection length remains almost unchanged
%         \item<2|only@2> AUG: As for the case of constant B$_t$ we have
%           pretty reproducible behavior matching basically the plasma
%           condition in within the current scan
%         \item<3|only@3> TCV: Even at such an high density at lower
%           current (and lower B$_t$) no sign of target ion flux
%           rollover/detachment
%         \item<4|only@4> AUG: Divertor neutral density exhibits 
%           the same behavior if considered as a function of greenwald fraction
%         \item<5|only@5> For AUG upstream and target profiles still
%           exhibit flattening earlier in density at lower current but
%           \alert{always at large values of 
%           $\Lambda_{div}$}. For TCV no sign of upstream profile flattening \alert{even
%             at very large values of $\Lambda_{div}$}
%         \item<6|only@6> This is due to the fact we did not reach
%           divertor detachment which \alert{seems mandatory for
%             upstream profile modification}  
%         \item<7|only@7> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
%           still reconcile the explored current scan
%         \item<8|only@8> AUG exhibit consistently an increase of
%           $\lambda_n$ with blob-size whereas for TCV the profile
%           remains flat consistently with a small variation of
%           $\delta_b$
%         \item<9|only@9> And for TCV this is true even at high value of
%           $\Lambda_{div}$. \alert{$\Lambda_{div}$ is not sufficient to
%           guarantee flat profiles on TCV.}
%       \end{itemize}
%     \end{column}
%   \end{columns}
% \end{frame}

@@

% \begin{frame}{H-Mode analysis on AUG}
%     \Fontvi
%   \vspace{-1cm}
%   \begin{columns}
%   \begin{column}{0.55\textwidth}
%     \centering{\includegraphics<1>[height=0.8\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralComparisonShot34276_34278_34281.pdf}}
%     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278_34281}}
%   \centering{\includegraphics<3>[height=0.75\textheight]{../../Experiments/AUG/analysis/pdfbox/UpstreamDivertorProfiles34276_34278_34281}}
%   \centering{\includegraphics<4>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278}}
%   \centering{\includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278_34281}}
%   \end{column}
%   \begin{column}{0.45\textwidth}
%     \begin{itemize}
%     \item<1|only@1> We perform a series of shots in H-Mode with 6.5
%       total heating power where we changed the fueling and the
%       efficiency of cryopumps. Specifically we have
%       \begin{itemize}
%         \item<1|only@1>\textcolor{colorA}{\# 34276 without the
%             cryompumps}
%         \item<1|only@1> \textcolor{colorB}{\# 34278 with the same
%             fueling as \# 34276 but with the cryompump}
%         \item<1|only@1> \textcolor{colorC}{\#34281 where we increase
%             fueling and seeding trying to mimic the same subdivertor
%             pressure as \# 34276}
%       \end{itemize}
%     \item<1|only@1> Keeping the same fueling with the cryopump clearly
%       reduce the pressure in the the sub-divertor area, we don't reach
%       clear detachment and the edge density is constant even during
%       the fueling ramp. Degraded H-mode reached later without the cryopump

%     \item<2|only@2> Different behavior of ELM during the fueling
%       ramp. ELM size and frequency changes strongly without the
%       cryopump or during extreme fueling case
%     \item<3|only@3> The profiles for shot \# 34278 with the cryopum
%       and lower fueling remains more steep in all the three timing
%       wind and the plasma is still attached. Interestingly for shot \#
%       34281 with the cryopumps and higher fueling the detachment is
%       more pronounced
%     \item<4|only@4> Without the cryopumps, we reached flatter
%          profiles with comparable inter-ELM resolved blob-size. This
%          indicates strong neutral pressure effects in determining
%          upstream profiles
%     \item<5|only@5> Increasing the fueling and correspondingly the
%       divertor neutral pressure move towards a situation similar to
%       \# 34276 without the cryopump
%       \end{itemize}
%   \end{column}
% \end{columns}
% \end{frame}

>>>>

      \includegraphics<1>[width=\textwidth]{~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}

@@

      \includegraphics<9>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeTargetVsDensityConstantBt}
      \includegraphics<10>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeTargetVsGreenwaldConstantBt}      
      \includegraphics<11>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeVsLambdaConstantBt}
      \includegraphics<12>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldBlobConstantBt}         
      \includegraphics<13>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldLambdaConstantBt}         

@@

          current in the far SOL. Amplitude starts increasing close to
          the transition to highly-recycling regime in analogy to
          JET HT \parencite{Wynn:2018gp} \onslide<10>{\alert{but once evolution \textit{vs} greenwald

@@

        \item<only@11> Amplitude evolution reconciled in AUG if

@@

        \item<only@12> For both AUG and TCV $\lambda_n$ increases
          with blob size without significant difference within the
          current explored
        \item<only@13> \alert{The evaluation of $\lambda_n$ as a
          function of $\Lambda_{div}$ confirms that this variable is
          insufficient to completely reconcile AUG and TCV}

@@

\begin{frame}{Current scan at constant q$_{95}$}
      \includegraphics<1>[width=\textwidth]{~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
      \includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsDensityConstantQ95}
      \includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationGreenwaldConstantQ95}
      \includegraphics<6>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantQ95}
      \includegraphics<8>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeTargetVsGreenwaldConstantBt}
      \includegraphics<9>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeVsLambdaConstantBt}
      \includegraphics<10>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldBlobConstantQ95}         
      \includegraphics<11>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldLambdaConstantQ95}         
        \item<1|only@1> Shape matched in within the single scan even
          though this required for TCV operation with very low
          toroidal field (0.8T)
        \item<1|only@1> The parallel connection length remains almost unchanged
        \item<2|only@2> AUG: As for the case of constant B$_t$ we have
          pretty reproducible behavior matching basically the plasma
          condition in within the current scan
        \item<3|only@3> TCV: Even at such an high density at lower
          current (and lower B$_t$) no sign of target ion flux
          rollover/detachment
        \item<4|only@4> Again for AUG peak target density rollover
          occurs at lower density for lower current as well as
          radiation front movement. For TCV rollover achieved only at
          higher current whereas lower I$_p$ does not exhibit sign of
          detachment even if high density is
          achieved. \alert{Consistent with lack of signature of
            volumetric recombination from DSS}
         \item<only@5> Interestingly considering the behavior as a
           function of greenwald fraction does not reconcile the
           different current neither on AUG.  
        \only<6-7>{\item For AUG upstream and target profiles still
          exhibit flattening earlier in density at lower current but
          \alert{always at large values of 
          $\Lambda_{div}$}. For TCV no sign of upstream profile flattening \alert{even
          at very large values of $\Lambda_{div}$}
        \item<only@7>  This is due to the fact we did not reach
          divertor detachment which \alert{seems mandatory for
            upstream profile modification}  
        \item<only@8> AUG: Amplitude evolution as a function of
          greenwald fraction confirms that shoulder starts appearing
          at the onset of highly recycling regime 
        \item<only@9> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
          still reconcile the explored current scan
        \item<only@10> AUG exhibit consistently an increase of
          $\lambda_n$ with blob-size whereas for TCV the profile
          remains flat consistently with a small variation of
          $\delta_b$
        \item<only@11> And for TCV this is true even at high value of
          $\Lambda_{div}$. \alert{$\Lambda_{div}$ is not sufficient to
          guarantee flat profiles on TCV.}

@@

\begin{frame}{H-Mode analysis on AUG}
    \Fontvi
  \vspace{-1cm}
  \begin{column}{0.55\textwidth}
    \centering{\includegraphics<1>[height=0.8\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralComparisonShot34276_34278_34281.pdf}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278_34281}}
  \centering{\includegraphics<3>[height=0.75\textheight]{../../Experiments/AUG/analysis/pdfbox/UpstreamDivertorProfiles34276_34278_34281}}
  \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278}}
  \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278_34281}}
  \begin{column}{0.45\textwidth}
    \item<1|only@1> We perform a series of shots in H-Mode with 6.5
      total heating power where we changed the fueling and the
      efficiency of cryopumps. Specifically we have
        \item<1|only@1>\textcolor{colorA}{\# 34276 without the
            cryompumps}
        \item<1|only@1> \textcolor{colorB}{\# 34278 with the same
            fueling as \# 34276 but with the cryompump}
        \item<1|only@1> \textcolor{colorC}{\#34281 where we increase
            fueling and seeding trying to mimic the same subdivertor
            pressure as \# 34276}
    \item<1|only@1> Keeping the same fueling with the cryopump clearly
      reduce the pressure in the the sub-divertor area, we don't reach
      clear detachment and the edge density is constant even during
      the fueling ramp. Degraded H-mode reached later without the cryopump

    \item<2|only@2> Different behavior of ELM during the fueling
      ramp. ELM size and frequency changes strongly without the
      cryopump or during extreme fueling case
    \item<3|only@3> The profiles for shot \# 34278 with the cryopum
      and lower fueling remains more steep in all the three timing
      wind and the plasma is still attached. Interestingly for shot \#
      34281 with the cryopumps and higher fueling the detachment is
      more pronounced
    \item<4|only@4> Without the cryopumps, we reached flatter
         profiles with comparable inter-ELM resolved blob-size. This
         indicates strong neutral pressure effects in determining
         upstream profiles
    \item<5|only@5> Increasing the fueling and correspondingly the
      divertor neutral pressure move towards a situation similar to
      \# 34276 without the cryopump
      \end{itemize}
  \end{column}
\end{columns}
\end{frame}
